\documentclass[10pt,a4paper]{article}
\usepackage[left=1.3cm,right=1.3cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{amsmath}
\setlength{\parindent}{0pt}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.3em}{0.3em}

% Bullet formatting: solid black circles
\setlist[itemize]{nosep, leftmargin=*, label=\textbullet}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\fontsize{20}{28}\selectfont \textbf{Shanshan Zhu}} \\[0.8em]
    {\large
    E-mail: zhushanshan0717@gmail.com \ \textbar\ 
    \href{https://github.com/shanshan717}{github.com/shanshan717}
    }
\end{center}

\vspace{1 em} 

\section*{EDUCATION}
\textbf{Nanjing Normal University} \hfill \textit{Nanjing, China} \\
M.Sc. in Psychology \hfill \textit{Exp. Jun 2026} \\
\textit{Core Courses: Experimental Psychology, R Programming in Psychology, Advanced Research Methods, Bayesian Statistics}

\vspace{0.8 em} 

\textbf{Hangzhou Normal University} \hfill \textit{Hangzhou, China} \\
B.A. in Health Services and Management \hfill \textit{Jun 2023} \\
\textit{Core Courses: Medical Statistics, Epidemiology, Clinical Medicine, Behavioral Medicine}

\vspace{1 em} 

\section*{RESEARCH EXPERIENCE}
\textbf{A Cognitive Ontological Dataset for Self-Referential Processing} \hfill \href{https://www.scidb.cn/en/detail?dataSetId=1b53c91112024d71b95c42bbd748141f&version=V4}{[Science Data Bank]} \\
\textit{Principal Investigator} \hfill \textit{Jan 2023 – Present}
\begin{itemize}
    \item Curated and shared an fMRI dataset on self-referential processing.
    \item Conducted systematic literature review, data standardization, and codebook revision.
    \item Expanded dataset to include psychiatric populations and lifespan samples.
\end{itemize}

\textbf{Neuroimaging Meta-Analysis of Self-Referential Processing Across Disorders} \\
\textit{Lead Researcher} \hfill \textit{Nov 2024 – Present}
\begin{itemize}
    \item Conducted coordinate-based meta-analysis (ALE) using \textbf{NiMARE}.
    \item Performed visualization with \textbf{Nilearn} and \textbf{Connectome Workbench}.
    \item Pre-registered on OSF: \href{https://osf.io/8rx4a/}{osf.io/8rx4a}.
\end{itemize}

\textbf{Python-Based fMRI Data Analysis Chinese Pipeline} \hfill \href{https://github.com/shanshan717/fMRI_Pipeline.git}{[GitHub]} \\
\textit{Lead Researcher} \hfill \textit{Sep 2024 – Present}
\begin{itemize}
    \item Developed open-source pipeline for: DICOM–NIfTI (BIDS, heudiconv), surface mapping, preprocessing (fMRIPrep), QC (MRIQC), GLM and MVPA (Nilearn, Brainstats).
    \item Authored tutorials tailored for non-native English speakers.
\end{itemize}

\textbf{Self-Reference Modulates Stimulus Representations in Visual Cortex} \\
\textit{Undergraduate Thesis Project} \hfill \textit{March 2024 – Present}
\begin{itemize}
    \item Designed and programmed block-design tasks in \textbf{PsychoPy}.
    \item Conducted fMRI data acquisition as scanner operator.
    \item Performed MVPA analysis of visual cortical representations.
\end{itemize}

\textbf{The Impact of Legal Professional Education on Moral and Legal Reasoning} \\
\textit{Research Assistant} \hfill \textit{Sep 2023 – Present}
\begin{itemize}
    \item Conducted preprocessing and GLM analysis using \textbf{Nilearn}.
    \item Performed gPPI analysis with \textbf{MATLAB (CONN toolbox)}.
    \item Contributed to group-level interpretation and manuscript.
\end{itemize}

\vspace{1 em} 

\section*{TEACHING EXPERIENCE}
\textbf{Bayesian Methods in Psychology} \hfill Teaching Assistant \hfill \textit{Spring 2024} \\
\textit{Supervisor: Prof. Chuan-Peng Hu, Nanjing Normal University}
\begin{itemize}
    \item Led tutorials and labs on Bayesian modeling using \textbf{PyMC}.
    \item Provided technical support to graduate students.
\end{itemize}

\vspace{1 em} 

\section*{PROFESSIONAL EXPERIENCE}
\textbf{Chinese Child Brain Development Project} \hfill MRI Technician \hfill \textit{Oct 2024 – Present}
\begin{itemize}
    \item Certified MRI operator; acquired structural, functional, and diffusion scans for children (ages 6–8).
    \item Ensured longitudinal neuroimaging data quality control.
\end{itemize}

\textbf{Institute of Psychology, Chinese Academy of Sciences} \hfill Trainee \hfill \textit{Jul 2024}
\begin{itemize}
    \item Completed one-week intensive training in \textbf{FSL} neuroimaging analysis.
\end{itemize}

\textbf{NetEase Intelligence} \hfill AI Trainer Intern \hfill \textit{May – Sep 2023}
\begin{itemize}
    \item Annotated and curated NLP corpora for LLM training.
    \item Improved dataset quality using cognitive-linguistic principles.
\end{itemize}

\textbf{Affiliated Hospital of Zhejiang University School of Medicine (Sir Run Run Shaw Hospital)} \hfill Research Intern \hfill \textit{Jul – Dec 2022}
\begin{itemize}
    \item Assisted with research administration, ethics review, and documentation.
\end{itemize}

\textbf{Affiliated Hospital of Hangzhou Normal University} \hfill Medical Observer \hfill \textit{Jul – Sep 2021}
\begin{itemize}
    \item Gained early clinical exposure in psychiatry and behavioral health units.
\end{itemize}

\vspace{1 em} 

\section*{CONFERENCES AND PRESENTATIONS}
\textbf{24th National Congress of Psychology} \hfill Chengdu, China \\
Oral Presentation: \textit{Abnormal Brain Activity in Self-Referential Processing Among Psychiatric Patients} \hfill \textit{Oct 2023}

\textbf{Cognitive Neuroscience Summer Hackathon} \hfill Hangzhou, China \\
Project Leader \hfill \textit{Aug 2024} 
\begin{itemize}
    \item Led Python-based fMRI pipeline development project.
\end{itemize}

\textbf{Cognitive Neuroscience Summer Hackathon} \hfill Shenzhen, China \\
Contributor \hfill \textit{Aug 2025}
\begin{itemize}
    \item Contributed to EEG-based emotion decoding project.
\end{itemize}

\vspace{1 em} 

\section*{ACADEMIC SERVICE}
\textbf{Chinese Open Science Network} \hfill \textit{2023 – Present} 
\begin{itemize}
    \item Academic Secretary: supported planning and organization of scholarly activities.
    \item WeChat Content Editor: produced and published articles promoting open science.
\end{itemize}

\vspace{1 em} 

\section*{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{Programming:} Python (primary), R, MATLAB 
    \item \textbf{Neuroimaging:} fMRIPrep, MRIQC, Connectome Workbench, FSL (certified), ALE meta-analysis, NiMARE, Nilearn, Brainstats
    \item \textbf{Tools:} GitHub, Docker, Jupyter, LaTeX, Microsoft Office
    \item \textbf{Languages:} English, Chinese (native)
\end{itemize}

\vspace{1 em} 

\section*{INTERESTS}
Long-distance running (half-marathons), rock climbing

\end{document}
