\documentclass[a4paper,10pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{fontawesome}

% Set up font and line spacing
\renewcommand{\baselinestretch}{1.2}
\renewcommand{\familydefault}{\sfdefault}

% Customizing section titles
\titleformat{\section}[block]{\normalfont\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}[runin]{\normalfont\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}[runin]{\normalfont}{\thesubsubsection}{1em}{}

% Header information
\pagestyle{fancy}
\fancyhead[L]{\textbf{Shanshan Zhu}}
\fancyhead[R]{\href{mailto:zhushanshan0717@gmail.com}{zhushanshan0717@gmail.com} | \href{https://github.com/shanshan717}{github.com/shanshan717}}

% Begin document
\begin{document}

% Name
\begin{center}
    \Huge \textbf{Shanshan Zhu} \\[0.5em]
    \small \href{mailto:zhushanshan0717@gmail.com}{zhushanshan0717@gmail.com} | \href{https://github.com/shanshan717}{github.com/shanshan717}
\end{center}

% Education section
\section*{Education}
\noindent
\textbf{Nanjing Normal University}, Nanjing, China \\
\textit{M.Sc. in Basic Psychology} \hfill \textit{Sep 2023 -- Jun 2026 (Expected)} \\
\vspace{0.3em}
\textbf{Hangzhou Normal University}, Hangzhou, China \\
\textit{B.A. in Health Services and Management} \hfill \textit{Sep 2019 -- Jun 2023}

% Research Experience section
\section*{Research Experience}
\noindent
\textbf{Principal Investigator, Self-Reference Database} \hfill \textit{Jan 2023 -- Present} \\
- Led the construction and cleaning of a self-reference dataset shared on the Science Data Bank platform. \\
- Leading an ALE meta-analysis project using Python to synthesize neuroimaging findings on self-referential processing (In Progress). \\[0.5em]

\noindent
\textbf{Principal Investigator, fMRI Pipeline Tutorial (Chinese)} \hfill \textit{Jul 2024 -- Present} \\
- Authored a beginner-friendly fMRI data processing guide to support open science in neuroimaging. \\[0.5em]

\noindent
\textbf{MRI Technician, CCNP Project, Nanjing Site} \hfill \textit{Oct 2024 -- Jul 2025} \\
- Conducted MRI scans for school-age children and assisted in quality assurance for longitudinal neuroimaging data. \\[0.5em]

\noindent
\textbf{Research Assistant, Legal Education and Brain Function Study} \hfill \textit{Feb 2024 -- Present} \\
- Co-authored a paper and conducted fMRI preprocessing and analysis to explore the effects of legal education on cognition.

% Teaching Experience section
\section*{Teaching Experience}
\noindent
\textbf{Teaching Assistant, Bayesian Methods in Psychology} \hfill \textit{Sep 2024 -- Jan 2025} \\
Nanjing Normal University | Instructor: Prof. Chuan-Peng Hu \\
- Facilitated labs and tutorials, assisting students with R and Python-based Bayesian statistics.

% Professional Training section
\section*{Professional Training}
\noindent
\textbf{FSL Neuroimaging Analysis Workshop} \hfill \textit{Jul 2024} \\
Institute of Psychology, Chinese Academy of Sciences \\
- Completed a 1-week intensive training and received certification.

% Internship Experience section
\section*{Internship Experience}
\noindent
\textbf{AI Trainer Intern, NetEase Intelligence} \hfill \textit{May 2023 -- Sep 2023} \\
- Annotated NLP training data; contributed to cognitive-linguistic tasks and model performance. \\[0.5em]

\noindent
\textbf{Research Intern, Sir Run Run Shaw Hospital} \hfill \textit{Jul 2022 -- Dec 2022} \\
- Supported research administration; assisted with documentation and ethical reviews. \\[0.5em]

\noindent
\textbf{Medical Observer, Affiliated Hospital of HNU} \hfill \textit{Jul 2021 -- Sep 2021} \\
- Gained early exposure to clinical settings in psychiatry and behavioral health.

% Conferences and Presentations section
\section*{Conferences and Presentations}
\noindent
\textbf{24th National Congress of Psychology}, Chengdu, China \hfill \textit{Oct 2023} \\
- Oral presentation: "Abnormal Brain Activity in Self-Referential Processing Among Psychiatric Patients: An ALE Meta-Analysis" \\[0.5em]

\noindent
\textbf{Frontiers in Cognitive Neuroscience Hackathon}, Hangzhou, China \hfill \textit{Aug 2024} \\
- Initiator and lead: "Python-Based fMRI Data Analysis Pipeline"

% Academic Service section
\section*{Academic Service}
\noindent
\textbf{Chinese Open Science Network} \hfill \textit{2023 -- Present} \\
- Academic Secretary: Assisted with planning and coordination of scholarly activities. \\
- WeChat Content Editor: Responsible for formatting and publishing WeChat articles.

% Skills section
\section*{Skills}
\begin{itemize}[left=0pt, label=--]
    \item \textbf{Programming:} Python, R
    \item \textbf{Neuroimaging:} FSL (certified), fMRI preprocessing, ALE meta-analysis
    \item \textbf{Tools:} Microsoft Office, LaTeX, GitHub
\end{itemize}

\end{document}
